---
title: "covid 19"
author: "Madeleine Alseryani"
date: "Spring 2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>% mutate(across(where(is.character), as.factor))
```


### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex




Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

## We create two bar charts - one based on frequency and the other on percent, use ggplot commands to do this

```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```
  

In the first bar plot, we can guess that not many people are dying. Whereas, in the second bar plot, it looks like more males are dying than females. It looks like it is almost by twice the amount. 



  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

Thee numerical results show that 1.4% of females have died and 3% of males died. This is more than twice the amount of females that died.

## Inferential results 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
 Based off the fishers test, we can see that 25 females died whereas 44 males died. The p value which was p=0.0012 was very low and tells us that there is a significant different between males and females dying. The odds of a male dying are 2.3 to 1 which is drastic. 

## Conclusions

